---
title: "Getting Started with imagerExtara"
author: "Shota Ochi"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with imagerExtara}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, cache=FALSE, 
               comment=NA, verbose=TRUE, fig.width=5, fig.height=5, dev='jpeg',dev.args=list(quality=50))			   
```

**imagerExtra** provides several advanced functions for image processing.

I will introduce the functions briefly.

**imagerExtara** is based on **imager**.

See the vignettes of **imager** if you aren't familiar with **imager**.

<br />

# Preparation
Most of the functions of **imagerExtra** are for grayscale image.

See the vignette **Treating Color Image with imagerExtra** if you want to treat color image with imagerExtra.

Let's prepare a grayscale image.

```{r, fig.width=4, fig.height=4, message=FALSE, dev='jpeg'}
library(imagerExtra)
g <- grayscale(boats)
plot(g)
```

<br />

# Piecewise Affine Histogram Equalization

Piecewise Affine Equalization (PAE) enhances contrast of image.

PAE has three parameters: *N*, *smin*, and *smax*.

However, we should not change *smin*. See [Jose-Luis Lisani, et al., IPOL, 2 (2012), pp. 243-265.](https://doi.org/10.5201/ipol.2012.lps-pae) for detail.

That's why PAE has two parameters in practice.

## the parameter *N*
*N* controls how the input gray level will be mapped in the output image. 

We don't have a priori choice for *N*. You will tune *N* mainly.

PAE acts as Histogram Equalization if *N* is large.

```{r, fig.width=8, fig.height=8, dev='jpeg'}
layout(matrix(1:4, 2, 2))
plot(g, main = "Original")
plot(EqualizePiecewise(g, 2), main = "N = 2")
plot(EqualizePiecewise(g, 10), main = "N = 10")
plot(EqualizePiecewise(g, 1000), main = "N = 1000")
```

## the parameter *smax*
*smax* controls the upper limit of contrast stretching.

If you want to prevent excessive enhancement of contrast, you should make *smax* low.

<br />

# Simplest Color Balance

Simplest Color Balance (SCB) enhances contrast of image.

SCB assumes that objectives in image have moderate pixel values.

That's why SCB saturates a percentage *sleft* % of the pixels on the left side of the histogram, and a percentage *sright* % of the pixels on the right side of the histogram.

See [Nicolas Limare, et al., IPOL, 1 (2011), pp. 297-315.](https://doi.org/10.5201/ipol.2011.llmps-scb) for detail.

## the parameters *sleft* and *sright*
*sleft* is a saturation percentage of the pixels on the left side of the histogram.

*sright* is a saturation percentage of the pixels on the right side of the histogram.

## the parameter *range*
SCB applies affine transformation after saturating pixels.

*range* defines the output range.

Default of *range* is [0,255]. You may prefer [0,1].

```{r, fig.width=7, fig.height=7, dev='jpeg'}
layout(matrix(1:2, 1, 2))
plot(g, main = "Original")
plot(BalanceSimplest(g, 1, 1), main = "sleft = 1, sright = 1")
```

<br />

# Screened Poisson Equation

Screend Poisson Equalization (SPE) enhances contrast of image.

The distinction of SPE is that SPE corrects the inhomogeneous background of image.

See [Jean-Michel Morel, et al., IPOL, 4 (2014), pp. 16-29.](https://doi.org/10.5201/ipol.2014.84) for detail.

Note that the performance of this function is bad because the implementation of 2D DCT is not efficient.

## the parameter *lamda*

*lamda* controls how strong corrects inhomogeneous background of image.

SPE corrects inhomogeneous background strongly if *lamda* is large.

## the parameters *s* and *range*

SPE uses Simplest Color Balance. *s* and *range* are the parameters for Simplest Color Balance.

*s* is used as both *sleft* and *sright*.

```{r, fig.width=7, fig.height=7, dev='jpeg'}
layout(matrix(1:2, 1, 2))
plot(g, main = "Original")
plot(SPE(g, 1), main = "lamda = 1")
```

<br />

# DCT denoising

DCT denoising is a simple and effective denoising algorithm using local DCT thresholding.

See [Guoshen Yu, and Guillermo Sapiro, IPOL, 1 (2011), pp. 292-296.](https://doi.org/10.5201/ipol.2011.ys-dct) for detail.

## the parameter *sdn*

*sdn* is a standrd deviation of noise of image.

The noise is strongly denoised if *sdn* is large.

## the parameter *flag_dct16x16*

*flag_dct16x16* determiens window size of local patches. DCT denoising uses 8x8 windows or 16x16 window.

Larger window size does not bring significant improvement when noise level is low.

Larger window size outperforms significantly smaller window size when noise level is low.

```{r, fig.width=7, fig.height=7, dev='jpeg'}
noisy <- g + imnoise(dim = dim(g), sd = 0.1)
layout(matrix(c(1,3,2,4), 2, 2))
plot(g, main = "Original")
plot(noisy, main = "Noisy Boats")
DenoiseDCT(noisy, 0.1) %>% plot(., main = "Denoised (8x8 window)")
DenoiseDCT(noisy, 0.1, flag_dct16x16 = TRUE) %>% plot(., main = "Denoised (16x16 window)")
```

<br />

# Iterative Triclass Thresholding

Iterative triclass thresholding is an iterative thresholding technique.

We need to set a rule to stop iteration.

We have two options.
* set preset threshold (*stopval*)
* set repeat number (*repeatnum*)

## the parameter *stopval* and *repeatnum*

*stopval* determines a preset threshold to stop iteration.

*repeatnum* determines how many times we repeat.

```{r, fig.width=7, fig.height=7}
g <- grayscale(dogs)
layout(matrix(1:4, 2, 2, byrow = TRUE))
plot(g, main = "Original", axes=F)
ThresholdTriclass(g, stopval = 0.001) %>% plot(main = "stopval = 0.001", axes=F)
ThresholdTriclass(g, repeatnum = 1) %>% plot(main = "repeatnum = 1", axes=F)
ThresholdTriclass(g, repeatnum = 3) %>% plot(main = "repeatnum = 3", axes=F)
```